---
title: "impacts"
author: "Ben Best"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Study Area: GoMex

- [GCOOS Products :: Shoreline](http://gcoos.org/products/index.php/bathymetry/shoreline/)
    - [GSHHG - A Global Self-consistent, Hierarchical, High-resolution Geography Database](http://www.soest.hawaii.edu/pwessel/gshhs/index.html)

```{r shore, message=F}
library(sp)
library(rgdal)
library(raster)
shore = shapefile('downloads/GSHHS_f_GOM/GSHHS_f_GOM.shp')
plot(shore)
```

## Raw Impacts

* [Global Map of Human Impacts to Marine Ecosystems - Data | NCEAS](https://www.nceas.ucsb.edu/globalmarine/data)
* [Halpern et al (2015) Cumulative human impacts: raw stressor data | KNB](https://knb.ecoinformatics.org/#view/doi:10.5063/F1S180FS)

### download

```{r download, eval=F}
library(dataone) # install.packages("dataone")

options(dataone_token = readLines('.dataone_token'))
am = AuthenticationManager()
getTokenInfo(am)
cn = CNode("PROD")
q = query(cn, solrQuery=list(q="id:doi*", fq="id:doi\\:10.5063/F1S180FS"))
m = q[[1]]

# download tifs
for (doc in m$documents){ # doc = m$documents[[2]]
  url = sprintf('https://knb.ecoinformatics.org/knb/d1/mn/v2/object/%s', doc)
  zip = sprintf('downloads/%s.zip', doc)
  download.file(url, zip)  
  unzip(zip, exdir='downloads')
}
```

### crop

```{r crop, eval=F}
# project shoreline from geographic to Mollweide like raster
r_1 = raster(list.files('downloads','.*\\.tif$', full.names = T)[1])
shore_mol = spTransform(shore, crs(r_1))

for (tif in list.files('downloads','.*\\.tif$', full.names = T)){ # tif = list.files('downloads','.*\\.tif$', full.names = T)[1]
  r_g = raster(tif)
  r_mol = crop(r_g, extent(shore_mol))
  writeRaster(r_mol, sprintf('tif_mol/%s', basename(tif)))
}
```

### plot

```{r plot}
# project shoreline from geographic to Mollweide like raster
r_1 = raster(list.files('tif_mol','.*\\.tif$', full.names = T)[1])
shore_mol = spTransform(shore, crs(r_1))

# loop through tifs
for (tif in list.files('tif_mol','.*\\.tif$', full.names = T)){ # tif = list.files('tif_mol','.*\\.tif$', full.names = T)[1]
  r = raster(tif)
  plot(
    r, main = tools::file_path_sans_ext(basename(tif)),
    col=rev(colorRampPalette(RColorBrewer::brewer.pal(n=9,'Spectral'))(256)))
  plot(shore_mol, add=T)
}
```

## Cumulative Impact Analysis

- [OHI-Science/cumimpacts: ArcGIS toolbox for Cumulative Impacts Analysis](https://github.com/OHI-Science/cumimpacts)
